### 2014-10-31 fundamentals/examples.tex
fixed in other branch

The early success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus posesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by user-developers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
\item the tools in the \Cyclus toolkit
\item and other tools for \Cyclus optimization, parallelization, and development.
\end{itemize}
All together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosytem.

Already, the ecosystem is growing. Early cross-institutional contributions to 
the ecosystem demonstrate a significant acheivement by the \Cyclus framework 
and provide hope for a community-driven development model.

@@

A number of projects and tools outside of the core simulation kernel have been 
developed which improve the scope and the diversity of the capabilities in the \Cyclus 
ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
under close integration with the \Cyclus kernel.
\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous Integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools outside of the scope of the \Cyclus kernel have been 
developed for improved user, developer, and analyst experinces with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Brite-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_nuclear_2014} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse 
needs of researchers at various institutions. These archetypes, contributed 
outside of the \Cyclus core and \Cycamore libraries are the first demonstration 
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

@@

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources dilineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange makes it easy for a reactor to
preferrentially accept recycled MOX fuel over fresh UOX fuel.  The
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was used.  This fabrication facility
mixes fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the Cosi fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flowmodopen}.

@@

To switch to a fully closed fuel cycle, all that needs to be done is change
the output commodity for the \Class{BatchReactor}'s spent MOX fuel.  All this
requires is a one-word change in the input file:

@@

This results in new the material flows in Figure \ref{fig:flowclosed}. Note
that because the \Class{BatchReactor} always transmutes fuel into the same
composition, the nuclide level flows are not very realistic for the full, multipass
recycle case.

>>>>

The early success of the \Cyclus simulator can be measured in many ways. 
The most compelling are demonstrations of the feasibility of the \Cyclus community-driven development 
model and of fundamental simulation capability. Nascent, promising growth of the \Cyclus 
ecosystem at multiple institutions indicates that a fuel cycle simulator can 
advance in a community-drive development paradigm. Additionally, simple 
simulations as well as more complex recycling simulations demonstrate that 
\Cyclus possesses fundamental fuel cycle simulation capabilities.

@@

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by user-developers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
\item the tools in the \Cyclus toolkit
\item and other tools for \Cyclus optimization, parallelization, and development.
\end{itemize}
All together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosystem.

Already, the ecosystem is growing. Early cross-institutional contributions to 
the ecosystem demonstrate a significant achievement by the \Cyclus framework 
and provide hope for a community-driven development model.

@@

A number of projects and tools outside of the core simulation kernel have been 
developed which improve the scope and the diversity of the capabilities in the \Cyclus 
ecosystem. Table \ref{tab:coretools} lists the tools and projects developed 
under close integration with the \Cyclus kernel.
\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Cycic &  Input control - embedded in Cyclist & \cite{flanagan_input_2013}\\
Cyclist & Interactive data exploration environment & \cite{livnat_cyclist_2014} \\
Ciclus & Continuous Integration scripts for \Cyclus & \cite{scopatz_ciclus_2014}\\
Cycstub & Skeleton for clean slate module development & \cite{carlsen_cycstub_2014}\\
Cyan & \Cyclus analysis tool & \cite{carlsen_cyan_2014}\\
Cloudlus & Tools for running \Cyclus in a cloud environment & \cite{carlsen_cloudlus_2014} \\
\hline
\end{tabularx}
\caption{Many tools outside of the scope of the \Cyclus kernel have been 
developed for improved user, developer, and analyst experiences with \Cyclus.}
\label{tab:coretools}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|X|r|}
\hline
\textbf{Name} & \textbf{Description} & \textbf{Citation} \\
\hline
Bright-lite & A physics-based reactor archetype and fuel fabrication archetype & \cite{flanagan_bright-lite_2014} \\
Nuclear Fuel Inventory Model & A flexible, ORIGEN-based, reactor analysis module & \cite{skutnik_nuclear_2014} \\
CommodConverter & A simple commodity converting storage facility archetype  & \cite{huff_commodconverter_2014} \\
MktDrivenInst & An institution that controls deployment based on commodity availability & \cite{huff_mktdriveninst_2014} \\
SeparationsMatrix & A facility for elemental separations of used fuel & \cite{huff_streamblender_2014} \\
StreamBlender & A facility for fuel fabrication from reprocessed streams & \cite{huff_streamblender_2014} \\
\hline
\end{tabularx}
\caption{A diverse set of archetypes under development reflect the diverse 
needs of researchers at various institutions. These archetypes, contributed 
outside of the \Cyclus core and \Cycamore libraries are the first demonstration 
of community-driven development in a fuel cycle simulator.}
\label{tab:archetypes}
\end{table}

@@

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources delineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The dynamic resource exchange makes it easy for a reactor to
preferentially accept recycled MOX fuel over fresh UOX fuel.  The
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

@@

The \Class{Source} and \Class{Sink} modules from \Cycamore were also used as a
source of fresh, enriched uranium and a repository respectively. A simple
custom recycled fuel fabrication facility was used.  This fabrication facility
mixes fissile and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in figure
\ref{fig:flowmodopen}.

@@

Simply changing the output commodity name of spent \gls{MOX} fuel from the 
\Class{BatchReactor} transforms this simulation into a closed fuel cycle. Only 
a one-word change in the input file:

@@

This results in new the material flows in Figure \ref{fig:flowclosed}. Note
that because the \Class{BatchReactor} always transmutes fuel into the same
composition, the nuclide level flows are not very realistic for the full, 
multi-pass
recycle case.

### 2014-10-31 fundamentals/impl.tex
fixed in other branch

\Cyclus, on the other hand, is primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms. 
Furthermore, the core infrastructure and related archetypes are free and 
open source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. It can be easily deployed 
on large computer systems, such as \acrlong{HTC} systems.

@@

The core of the \Cyclus simulator creates a set of key classes on which agent 
plug-ins 
are based. In addition, a set of key tools are also provided to enrich the 
\gls{API} and supply a robust suite of behaviors for the developer.

@@

Agent plug-ins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on the dynamic loading and paradigm for clean plug-in 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

@@

A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
architecture into a suite of dynamically loadable plug-in libraries.  Though 
common in modern software architecture, such a plug-in pattern has 
previously not been implemented in nuclear fuel cycle simulators in the 
literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
object-oriented \gls{API} and modern build system already described.

Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation: the core of the code operates
completely independently from the individual plug-in libraries. Thus, any
customization or extension is implemented only in the loadable
library.

@@

In particular, since the clean plug-in architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open source archetypes. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

@@

\subsection{Agent Interchangability}\label{sec:interchangeability}

Due to this plug-in architecture,
implementations of actors in a given simulation can be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be compared to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

Interchangability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./images/agent_uml}
\end{center}
\caption{The inheritance in \Cyclus classes, such as the \Class{Agent}, 
\Class{Facility}, \Class{Institution}, and \Class{Region} classes abstract away 
unneccesary details while exposing powerful functionality. In the above 
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in 
order to become a bonified Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

@@

Two primary consequences arise from this structure. First, institutions are
responsible for building and decommissioning facilities, so advanced
logic regarding building and decommissioning can be obtained by subclassing the
\Class{Institution} interface. Second, the \Class{Facility} class implemenets the
\Class{Trader} interface, and thus institutions and regions can
adjust the resource flow preferences of their managed facilities, respectively. Importantly,
this novel capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Agent Type} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Institution & ManagerInst & The manager institution manages production of commodiites among its facilities by building new necessary ones. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
\label{tab:cycamore}
\end{table}

>>>>

\Cyclus, on the other hand, is primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms. 
Furthermore, the core infrastructure and related archetypes are free and 
open source, BSD-3-clause licensed. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. It can be easily deployed 
on large computer systems, such as \acrlong{HTC} systems.

@@

The core of the \Cyclus simulator creates a set of key classes on which agent plugins 
are based. In addition, a set of key tools are also provided to enrich the 
\gls{API} and supply a robust suite of behaviors for the developer.

@@

Agent plugins utilize the generic core \gls{API} to interact with one another.  For 
example, agents rely on the dynamic loading and paradigm for clean plugin 
behavior at the start of the simulation. They also use the resource exchange 
paradigm \gls{API} for trading resources with one another.

@@

A key innovation in \Cyclus is implementing this generic \gls{API} and modular 
architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
common in modern software architecture, such a ``plugin'' pattern has 
previously not been implemented in nuclear fuel cycle simulators in the 
literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
object-oriented \gls{API} and modern build system already described.

Dynamically loadable libraries are the primary mechanism for extending \Cyclus' capability. 
This approach provides encapsulation: the core of the code operates
completely independently from the individual plugin libraries. Thus, any
customization or extension is implemented only in the loadable
library.

@@

In particular, since the clean plugin architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open-source archetypes. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

@@

\subsection{Agent Interchangeability}\label{sec:interchangeability}

Due to this ``plugin'' architecture,
implementations of actors in a given simulation can be easily
interchanged. Critically, this novel functionality enables the comparison
between agent implementations. For example, a low-physics-fidelity
implementation of a reactor can be compared to an implementation with higher
physics fidelity, allowing an analyst to discern the effect of reactor physical
fidelity on a given fuel cycle.

Interchangeability is accomplished by providing \glspl{API} that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchical relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./images/agent_uml}
\end{center}
\caption{The inheritance in \Cyclus classes, such as the \Class{Agent}, 
\Class{Facility}, \Class{Institution}, and \Class{Region} classes abstract away 
unnecessary details while exposing powerful functionality. In the above 
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in 
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

@@

Two primary consequences arise from this structure. First, institutions are
responsible for building and decommissioning facilities, so advanced
logic regarding building and decommissioning can be obtained by sub-classing the
\Class{Institution} interface. Second, the \Class{Facility} class implements the
\Class{Trader} interface, and thus institutions and regions can
adjust the resource flow preferences of their managed facilities, respectively. Importantly,
this novel capability allows for the modeling of preferential regional trading
of resources (e.g., tariffs) as well as preferential institutional trading
(e.g., long-term contracts).

@@

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Agent Type} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & BatchReactor & A reactor model that handles batch refuelling, based on pre-determined recipes of compositions. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new necessary ones. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple simulation use cases.}
\label{tab:cycamore}
\end{table}

### 2014-10-31 fundamentals/intro.tex
fixed in other branch

The \Cyclus Nuclear Fuel Cycle Simulator framework and 
its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
simulator. This dynamic simulator employs discrete agents, time, and materials 
up to isotopic resolution in order to support a range of analysis types, levels of 
detail, and fuel cycle analysts.
Additionally, \Cyclus employs a modular architecture and 
open development process that supports user access and 
encourages developer extensions.

@@

Nuclear fuel cycle simulators can drive \gls{RDD} by calculating `metrics', 
quantitative measures of performance that 
can be compared among fuel cycle options. The feasibility of technology 
strategies, dynamics of transitions between fuel cycles, and many other 
measures of performance can be expressed in terms of these metrics. For example, 
economic feasibility is often measured in \gls{LCOE}
while environmental performance might be measured in spent fuel volume, 
  toxicity, or mined uranium.

@@

Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a multiscale problem, but existing tools are not sufficiently 
multiscale. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition of fast reactor fuel. Each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels challenging within a single tool. 
However, an extensible architecture and discrete object tracking allow 
the creation and exchangeability of custom \Cyclus archetypes at any level of fidelity.

@@

There are a number of types of users and developers who will 
interact with the \Cyclus framework. National laboratory researchers,
academic researchers, private-industry economic forcasters, and even students 
in engineering courses may benefit from the ease of development and
customization provided by the modular architecture of \Cyclus.

@@

\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and takes advantage of modern computing resources.  
Furthermore, \gls{ABM} provides an analyst a more natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context for example, an analyst can design an agent with reactor-related logic 
entirely independent from a separate agent with fuel fabrication-related 
logic. Defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bonafide actors in the simulation.  The two archetype libraries, therefore, need 
not have any shared knowledge of one another for them to be building blocks in 
the same simulation.

>>>>

The \Cyclus Nuclear Fuel Cycle Simulator framework and 
its modeling ecosystem answer this need for a next generation nuclear fuel cycle 
simulator. Dynamic simulation of nuclear fuel cycles with discrete agents 
and up to isotopic resolution support 
levels of detail appropriate for a varied community of analysts
interested in a range of analysis types. Additionally, \Cyclus employs an 
open development process that supports user access and 
encourages developer extensions.

@@

Nuclear fuel cycle simulators can drive \gls{RDD} by calculating `metrics', 
quantitative measures of performance that 
can be compared among fuel cycle options. The feasibility of technology 
strategies, dynamics of transitions between fuel cycles, and many other 
measures of performance can be expressed in terms of these metrics. For example, 
economic feasibility is often measured in \gls{LCOE} while proliferation risk 
can be proportional to total kilograms of separated Pu, and environmental 
performance might be measured in spent fuel volume, toxicity, or mined uranium.

@@

Furthermore, modeling the evolution of a physics-dependent, international nuclear fuel supply
chain is a multiscale problem, but existing tools are not sufficiently 
multiscale. Tools have either focused on macro effects, e.g., the fleet-level
stocks and flows of commodities, or micro effects, e.g., the used fuel
composition of fast reactor fuel. Each focus has driven the
development of these tools, rendering the task of answering questions between
the macro and micro levels challenging within a single tool. 
However, an extensible architecture and discrete object tracking allow 
the creation and interchangeability of custom \Cyclus archetypes at any level of fidelity.

@@

There are a number of types of users and developers who will 
interact with the \Cyclus framework. National laboratory researchers,
academic researchers, private-industry economic forecasters, and even students 
in engineering courses may benefit from the ease of development and
customization provided by the modular architecture of \Cyclus.

@@

\Cyclus utilizes an \gls{ABM} paradigm.  \gls{ABM} is modern, sophisticated, 
true to reality, and takes advantage of modern computing resources.  
Furthermore, \gls{ABM} provides an analyst a more natural 
perspective from which to model a given problem. In the nuclear fuel cycle 
context for example, an analyst can design an agent with reactor-related logic 
entirely independent from a separate agent with fuel fabrication-related 
logic. Defining the behavior of both agents according to the 
\gls{API} contract is sufficient for them to interact with one another as 
bona fide actors in the simulation.  The two archetype libraries, therefore, need 
not have any shared knowledge of one another for them to be building blocks in 
the same simulation.
